---
title: "RPPA TCGA-SARC"
author: "Alicia Pliego"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 3
    number_sections: true
    theme: sandstone
---
\justify

# RPPA TCGA-SARC analysis

```{r , include=FALSE, echo=FALSE, message=FALSE}
library(ComplexHeatmap)
library(pheatmap)
library(limma)
library(plotly)
library(NMF)
library(Glimma)
library(edgeR)
library(tidyverse)
library(skimr)
library(uwot)
library(factoextra)
library(cowplot)
library(limma)
library(NMF)
library(pheatmap)
library(dplyr)
library(tsne)
library(RTCGA)
library(DT)
```

```{r , include=FALSE, echo=FALSE, message=FALSE}
tcga.sarc <- read.csv('data/RPPA_tcga_merged_annotations.txt', sep = '\t')
```

```{r normalization, include=FALSE, echo=FALSE, message=FALSE}
tcga.sarc2 <- tcga.sarc
tcga.sarc2$X <- NULL
tcga.sarc2$annotation <- NULL
tcga.sarc2$HRDscore <- NULL
n <- tcga.sarc2$patient_barcode
tcga.sarc2t <- as.data.frame(t(tcga.sarc2[,-1]))
colnames(tcga.sarc2t) <- n
tcga.sarc2t2<- t(tcga.sarc2t)
tcga.norm <- normalizeQuantiles(tcga.sarc2t2)
tcga.pca <- prcomp(tcga.norm)
HRDscore <- tcga.sarc$HRDscore
```
## tSNE for RPPA TCGA-SARC colored by HRD34 score
```{r umap, include=FALSE, echo=FALSE, message=FALSE}
tsne <- tsne(tcga.norm, initial_dims = 2)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width= 5, fig.height = 5, fig.align='center'}
tsne <- data.frame(tsne)
pdb <- cbind(tsne,tcga.sarc$HRDscore)
options(warn = -1)
fig <-  plot_ly(data = pdb ,x =  ~X1, y = ~X2, type = 'scatter', mode = 'markers', split = ~tcga.sarc$HRDscore)

fig <- fig %>%
  layout(
    plot_bgcolor = "#e5ecf6"
  )

fig
```


```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width= 5, fig.height = 5, fig.align='center'}
pdb <- cbind(tsne,tcga.sarc$annotation)
options(warn = -1)
fig <-  plot_ly(data = pdb ,x =  ~X1, y = ~X2, type = 'scatter', mode = 'markers', split = ~tcga.sarc$annotation)

fig <- fig %>%
  layout(
    plot_bgcolor = "#e5ecf6"
  )

fig
```


```{r limma, include=FALSE, echo=FALSE, message=FALSE}
#Run limma model in RPPA data
design <- model.matrix(~ 0 + HRDscore )

tcga.nmf.limma <- lmFit(t(tcga.norm), design = design)

head(coef(tcga.nmf.limma))
```


Data was downloaded from GDC Data Commons and was normalize by quantile normalization. 
Data was divided into two groups (HRDhigh/HRDlow) for comparison.
Linear regression was applies using the R package limma (@limma).

```{r , include=FALSE, echo=FALSE, message=FALSE}
#Make contrast and fit Bayes
contr <- makeContrasts(HRDscoreHRDhigh - HRDscoreHRDlow, levels = colnames(coef(tcga.nmf.limma)))
tmp <- contrasts.fit(tcga.nmf.limma, contr)
tmp <- eBayes(tmp)
```

```{r topgenes  ,include=FALSE, echo=FALSE, message=FALSE}
top.table <- topTable(tmp, sort.by = "P", n = Inf)
```


## Table of differentially expressed proteins in the HRDhigh group vs the HRDlow.

Table only shows proteins with an adjusted pvalue < 0.05.
  - Positive logFC indicates overexpressed and 
  - Negative logFC indicated underexpressed.

```{r ,  include=FALSE, echo=FALSE, message=FALSE}
top.table.filt <- top.table %>%
  filter(adj.P.Val <= 0.05) %>%
  arrange(adj.P.Val)
top_table_df <- as.data.frame(top.table.filt)
DT::datatable(top_table_df )
```

```{r , include=FALSE, echo=FALSE, message=FALSE}
t_tcga_norm <- t(tcga.norm)
mat <- t_tcga_norm[rownames(top.table.filt),]
mat.z <- t(apply(mat, 1, scale))
colnames(mat.z) <- rownames(tcga.norm)
```

## Heatmap Differentially expressed proteins HRDhigh vs HRDlow in all cases TCGA-SARC

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width= 14, fig.height = 9, fig.align='center'}
library(heatmaply)

heatmaply(t(mat.z), 
  scale_fill_gradient_fun = ggplot2::scale_fill_gradient2(
    low = "blue", 
    high = "red", 
    midpoint = 0.5, 
    limits = c(0, 1)
  ),
  showticklabels = c(TRUE, FALSE),
  scale = "row",
  main = "RPPA TCGA-SARC",
  row_side_colors = tcga.sarc[,c("HRDscore", "annotation")]
  )
```

```{r , include=FALSE, echo=FALSE, message=FALSE}
design <- model.matrix(~ 0 + as.factor(HRDscore))
tcga.nmf.limma <- lmFit(t(tcga.norm), design = design)
tcga.nmf.eb <- eBayes(tcga.nmf.limma)
top_table_nmf <- topTable(tcga.nmf.eb, n = Inf)
```

```{r , include=FALSE, echo=FALSE, message=FALSE}
top_table_nmf_filt <- top_table_nmf %>%
  filter(adj.P.Val <= 0.05) %>%
  arrange(adj.P.Val)

top_table_heatmap <- top_table_nmf_filt
top_table_nmf_filt$F <- NULL
top_table_nmf_filt$AveExpr <- NULL
top_table_nmf_filt$P.Value <- NULL
top_table_nmf_filt$adj.P.Val <- NULL
top_table_nmf_filt$HRDhigh <- top_table_nmf_filt$as.factor.HRDscore.HRDhigh
top_table_nmf_filt$HRDlow <- top_table_nmf_filt$as.factor.HRDscore.HRDlow
top_table_nmf_filt$as.factor.HRDscore.HRDhigh <- NULL
top_table_nmf_filt$as.factor.HRDscore.HRDlow  <- NULL
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width= 10, fig.height = 9, fig.align='center'}
library(heatmaply)

heatmaply(top_table_nmf_filt, 
  scale_fill_gradient_fun = ggplot2::scale_fill_gradient2(
    low = "blue", 
    high = "red", 
    midpoint = 0.5, 
    limits = c(0, 1)
  ),
  showticklabels = c(TRUE, TRUE),
  scale = "column",
  main = "Differentially Expressed proteins TCGA-SARC"
  )
```



---
nocite: '@*'
---
